*DCVtestkit*: an R package for analysis of quality control dilution curves

### 2022-10-13 Manuscript/manuscript.qmd
Add a news files.

-   The sentence should begin: 'This work was supported by ...' -
-   The full official funding agency name should be given, i.e. 'National Institutes of Health', not 'NIH' (full RIN-approved list of UK funding agencies)
-   Grant numbers should be given in brackets as follows: '[grant number xxxx]'
-   Multiple grant numbers should be separated by a comma as follows: '[grant numbers xxxx, yyyy]'
-   Agencies should be separated by a semi-colon (plus 'and' before the last funding agency)
-   Where individuals need to be specified for certain sources of funding the following text should be added after the relevant agency or grant number 'to [author initials]'.

An example is given here: 'This work was supported by the National Institutes of Health [AA123456 to C.S., BB765432 to M.H.]; and the Alcohol & Education Research Council [hfygr667789].'

>>>>

-   The sentence should begin: 'This work was supported by ...' -
-   The full official funding agency name should be given, i.e. 'National Institutes of Health', not 'NIH' (full RIN-approved list of UK funding agencies)
-   Grant numbers should be given in brackets as follows: '\[grant number xxxx\]'
-   Multiple grant numbers should be separated by a comma as follows: '\[grant numbers xxxx, yyyy\]'
-   Agencies should be separated by a semi-colon (plus 'and' before the last funding agency)
-   Where individuals need to be specified for certain sources of funding the following text should be added after the relevant agency or grant number 'to \[author initials\]'.

An example is given here: 'This work was supported by the National Institutes of Health \[AA123456 to C.S., BB765432 to M.H.\]; and the Alcohol & Education Research Council \[hfygr667789\].'
